Data_visualization

### 2018-08-03 Rmd/ggplot_2_species_trial.Rmd
last changes

---
title: ''
output:
  pdf_document: default
  html_document: default
---
```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=7,out.width='100%'}
#Preparing seed set plots, starting with Petunia

#There are 3 crosses were seeds were lost (2,7,9)
#load libraries
library(reshape2)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(grid)
library(lattice)
#read data and cleaning
pein_seed_set <- read.csv("Data/PEIN_seed_set.csv", sep=";")
#removing samples where seeds got lost, first ones of the experiment
pein_seed_set <- pein_seed_set[-c(42,47,49),]

#
##
###
#PETUNIA
###
##
#
#Removing RARA, species not considered because sterility

pein_seed_set <- filter(pein_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%")

#adding the focal species, first 50%
Species <- rep("PEIN", 10)
Treatment <- rep("PEIN 50%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
pein_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production,stringsAsFactors = F)
#adding the focal species, 100%
Species <- rep("PEIN", 10)
Treatment <- rep("PEIN 100%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
pein_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production,stringsAsFactors = F)
#Order from lower to higher values the average, to plot it nicely
pein_seed_set <- rbind(pein_seed_set, pein_50, pein_100)
pein_seed_set$Treatment<- as.character(pein_seed_set$Treatment)
pein_seed_set <- pein_seed_set[order(pein_seed_set$Treatment),]  
#Organizing with just 50% and cross, self, flower control and control on a side

library(stringr)
pein_seed_set_div <- str_split_fixed(as.character(pein_seed_set$Treatment), " ", 2)
pein_seed_set_div <- data.frame(pein_seed_set_div, stringsAsFactors = F)
colnames(pein_seed_set_div)=c("non_focal","percentage")
pein_seed_set_bind <- cbind(pein_seed_set,pein_seed_set_div)
pein_seed_set_bind <- filter(pein_seed_set_bind, percentage!="100%")
#Because I want to give it specifically order I do it separately
#pein_seed_set_common <- filter(pein_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))

pein_seed_set_cross <- filter(pein_seed_set_bind, non_focal %in% c("CROSS"))
pein_seed_set_self <- filter(pein_seed_set_bind, non_focal %in% c("SELF"))
pein_seed_set_control <- filter(pein_seed_set_bind, non_focal %in% c("CONTROL"))
pein_seed_set_flower <- filter(pein_seed_set_bind, non_focal %in% c("FLOWER"))

@@

# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("CROSS"),]
pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("SELF"),]
pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("CONTROL"),]
pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("FLOWER"),]

pein_seed_set_final<-rbind(pein_seed_set_bind,pein_seed_set_cross, pein_seed_set_self, pein_seed_set_control,
                           pein_seed_set_flower)
#deleting extra columns used for data formating
pein_seed_set_final=pein_seed_set_final[,-c(5,6)]
#adding NA'S to the focal species
pein_seed_set_final[pein_seed_set_final$Treatment==c("PEIN 50%"),4] <- NA
#changing non_focal species name
pein_seed_set_final$Treatment=as.character(pein_seed_set_final$Treatment)
pein_seed_set_final$Family[pein_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
pein_seed_set_final$Family[pein_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
pein_seed_set_final$Family[pein_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
pein_seed_set_final$Family[pein_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
pein_seed_set_final$Family[pein_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
pein_seed_set_final$Family[pein_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
pein_seed_set_final$Family[pein_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
pein_seed_set_final$Family[pein_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
pein_seed_set_final$Family[pein_seed_set_final$Treatment=="IPPU 50 %"] <- "Convolvulaceae"
pein_seed_set_final$Family[pein_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"

pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="IPPU 50 %"] <- "Ipomoea purpurea"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"

#Colur per family

a <- ggplot(pein_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Petunia integrifolia",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

#
##
###
#C. ANNUUM 
###
##
#
caan_seed_set <- read.csv("Data/CAAN_seed_set.csv", sep=";")

#adding the focal species, first 50%
Species <- rep("CAAN", 10)
Treatment <- rep("CAAN 50%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
caan_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
#adding the focal species, 100%
Species <- rep("CAAN", 10)
Treatment <- rep("CAAN 100%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
caan_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
#Order from lower to higher values the average, to plot it nicely
caan_seed_set <- caan_seed_set[,-4]
colnames(caan_seed_set)[1] <- "Species"
colnames(caan_seed_set)[2] <- "Treatment"
colnames(caan_seed_set)[3] <- "Treatment.number"
colnames(caan_seed_set)[4] <- "Seed.production"
caan_seed_set <- rbind(caan_seed_set, caan_50, caan_100)
caan_seed_set$Treatment<- as.character(caan_seed_set$Treatment)
caan_seed_set <- caan_seed_set[order(caan_seed_set$Treatment),]

@@

library(stringr)
caan_seed_set_div <- str_split_fixed(as.character(caan_seed_set$Treatment), " ", 2)
caan_seed_set_div <- data.frame(caan_seed_set_div, stringsAsFactors = F)
colnames(caan_seed_set_div)=c("non_focal","percentage")
caan_seed_set_bind <- cbind(caan_seed_set,caan_seed_set_div)
caan_seed_set_bind <- filter(caan_seed_set_bind, percentage!="100%")

#Because I want to give it specifically order I do it separately
#pein_seed_set_common <- filter(caan_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))

caan_seed_set_cross <- filter(caan_seed_set_bind, non_focal %in% c("CROSS"))
caan_seed_set_self <- filter(caan_seed_set_bind, non_focal %in% c("SELF"))
caan_seed_set_control <- filter(caan_seed_set_bind, non_focal %in% c("CONTROL"))
caan_seed_set_flower <- filter(caan_seed_set_bind, non_focal %in% c("FLOWER"))

@@

# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("CROSS"),]
caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("SELF"),]
caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("CONTROL"),]
caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("FLOWER"),]

caan_seed_set_final<-rbind(caan_seed_set_bind,caan_seed_set_cross, caan_seed_set_self, caan_seed_set_control,
                           caan_seed_set_flower)
#deleting extra columns used for data formating
caan_seed_set_final=caan_seed_set_final[,-c(5,6)]
#adding NA'S to the focal species
caan_seed_set_final[caan_seed_set_final$Treatment==c("CAAN 50%"),4] <- NA

#changing non_focal species name
caan_seed_set_final$Treatment=as.character(caan_seed_set_final$Treatment)
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="caan 50%"] <- "Solanaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"

caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"

#Different colour per family
b <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Capsicum annuum",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

#
##
###
#S. LYCOPERSICUM
###
##
#

soly_seed_set <- read.csv("Data/SOLY_seed_set.csv", sep=";")
soly_seed_set <- filter(soly_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )

#adding the focal species, first 50%
Species <- rep("SOLY", 10)
Treatment <- rep("SOLY 50%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
soly_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
#adding the focal species, 100%
Species <- rep("SOLY", 10)
Treatment <- rep("SOLY 100%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
soly_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
#Order from lower to higher values the average, to plot it nicely
soly_seed_set <- soly_seed_set[,-4]
colnames(soly_seed_set)[1] <- "Species"
colnames(soly_seed_set)[2] <- "Treatment"
colnames(soly_seed_set)[3] <- "Treatment.number"
colnames(soly_seed_set)[4] <- "Seed.production"
soly_seed_set <- rbind(soly_seed_set, soly_50, soly_100)
soly_seed_set$Treatment<- as.character(soly_seed_set$Treatment)
soly_seed_set <- soly_seed_set[order(soly_seed_set$Treatment),]

library(stringr)
soly_seed_set_div <- str_split_fixed(as.character(soly_seed_set$Treatment), " ", 2)
soly_seed_set_div <- data.frame(soly_seed_set_div, stringsAsFactors = F)
colnames(soly_seed_set_div)=c("non_focal","percentage")
soly_seed_set_bind <- cbind(soly_seed_set,soly_seed_set_div)
soly_seed_set_bind <- filter(soly_seed_set_bind, percentage!="100%")

#Because I want to give it specifically order I do it separately
#pein_seed_set_common <- filter(soly_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))

soly_seed_set_cross <- filter(soly_seed_set_bind, non_focal %in% c("CROSS"))
soly_seed_set_self <- filter(soly_seed_set_bind, non_focal %in% c("SELF"))
soly_seed_set_control <- filter(soly_seed_set_bind, non_focal %in% c("CONTROL"))
soly_seed_set_flower <- filter(soly_seed_set_bind, non_focal %in% c("FLOWER"))

# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("CROSS"),]
soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("SELF"),]
soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("CONTROL"),]
soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("FLOWER"),]

soly_seed_set_final<-rbind(soly_seed_set_bind,soly_seed_set_cross, soly_seed_set_self, soly_seed_set_control,
                           soly_seed_set_flower)
#deleting extra columns used for data formating
soly_seed_set_final=soly_seed_set_final[,-c(5,6)]
#adding NA'S to the focal species
soly_seed_set_final[soly_seed_set_final$Treatment==c("SOLY 50%"),4] <- NA

#changing non_focal species name
soly_seed_set_final$Treatment=as.character(soly_seed_set_final$Treatment)
soly_seed_set_final$Family[soly_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
soly_seed_set_final$Family[soly_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
soly_seed_set_final$Family[soly_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
soly_seed_set_final$Family[soly_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
soly_seed_set_final$Family[soly_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
soly_seed_set_final$Family[soly_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
soly_seed_set_final$Family[soly_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
soly_seed_set_final$Family[soly_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
soly_seed_set_final$Family[soly_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
soly_seed_set_final$Family[soly_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"

soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"

#Different colour per family
c <- ggplot(soly_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Solanum lycopersicum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

#
##
###
#S. MELONGENA
###
##
#

>>>>

---
title: ''
output:
  pdf_document: default
  html_document: default
---
```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=7,out.width='100%'}

library(reshape2)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(grid)
library(lattice)

#Preparing seed set plots, starting with Petunia
#
##
###
#I. AQUATICA
###
##
#

ipaq_seed_set <- read.csv("Data/ipaq_seed_set.csv", sep=";")
colnames(ipaq_seed_set)[1] <- "Species"
colnames(ipaq_seed_set)[2] <- "Treatment"
colnames(ipaq_seed_set)[3] <- "Treatment.number"
colnames(ipaq_seed_set)[4] <- "Seed.production"

ipaq_seed_set <- filter(ipaq_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )

#adding the focal species, first 50%
Species <- rep("IPAQ", 10)
Treatment <- rep("IPAQ 50%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
ipaq_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
#adding the focal species, 100%
Species <- rep("IPAQ", 10)
Treatment <- rep("IPAQ 100%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
ipaq_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
#Order from lower to higher values the average, to plot it nicely

ipaq_seed_set <- rbind(ipaq_seed_set, ipaq_50, ipaq_100)
ipaq_seed_set$Treatment<- as.character(ipaq_seed_set$Treatment)
ipaq_seed_set <- ipaq_seed_set[order(ipaq_seed_set$Treatment),]

library(stringr)
ipaq_seed_set_div <- str_split_fixed(as.character(ipaq_seed_set$Treatment), " ", 2)
ipaq_seed_set_div <- data.frame(ipaq_seed_set_div, stringsAsFactors = F)
colnames(ipaq_seed_set_div)=c("non_focal","percentage")
ipaq_seed_set_bind <- cbind(ipaq_seed_set,ipaq_seed_set_div)
ipaq_seed_set_bind <- filter(ipaq_seed_set_bind, percentage!="100%")

#Because I want to give it specifically order I do it separately
#pein_seed_set_common <- filter(ipaq_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))

ipaq_seed_set_cross <- filter(ipaq_seed_set_bind, Treatment %in% c("cross"))
ipaq_seed_set_self <- filter(ipaq_seed_set_bind, Treatment %in% c("self"))
ipaq_seed_set_control <- filter(ipaq_seed_set_bind, Treatment %in% c("control"))
ipaq_seed_set_flower <- filter(ipaq_seed_set_bind, Treatment %in% c("flower control"))

@@

# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
ipaq_seed_set_bind=ipaq_seed_set_bind[ipaq_seed_set_bind$Treatment!=c("cross"),]
ipaq_seed_set_bind=ipaq_seed_set_bind[ipaq_seed_set_bind$Treatment!=c("self"),]
ipaq_seed_set_bind=ipaq_seed_set_bind[ipaq_seed_set_bind$Treatment!=c("control"),]
ipaq_seed_set_bind=ipaq_seed_set_bind[ipaq_seed_set_bind$Treatment!=c("flower control"),]

ipaq_seed_set_final<-rbind(ipaq_seed_set_bind,ipaq_seed_set_cross, ipaq_seed_set_self, ipaq_seed_set_control,
                           ipaq_seed_set_flower)
#deleting extra columns used for data formating
ipaq_seed_set_final=ipaq_seed_set_final[,-c(5,6)]
#adding NA'S to the focal species
ipaq_seed_set_final[ipaq_seed_set_final$Treatment==c("IPPA 50%"),4] <- NA

#changing non_focal species name
ipaq_seed_set_final$Treatment=as.character(ipaq_seed_set_final$Treatment)
ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"

ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"

ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="cross"] <- "Cross"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="self"] <- "Self"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="control"] <- "Control"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="flower control"] <- "Flower control"

#Different colour per family
a <- ggplot(ipaq_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Ipomea aquatica",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

ippu_seed_set <- read.csv("Data/ippu_seed_set.csv", sep=";")
colnames(ippu_seed_set)[1] <- "Species"
colnames(ippu_seed_set)[2] <- "Treatment"
colnames(ippu_seed_set)[3] <- "Treatment.number"
colnames(ippu_seed_set)[4] <- "Seed.production"

ippu_seed_set <- filter(ippu_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )

#adding the focal species, first 50%
Species <- rep("IPPU", 10)
Treatment <- rep("IPPU 50%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
ippu_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
#adding the focal species, 100%
Species <- rep("IPPU", 10)
Treatment <- rep("IPPU 100%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
ippu_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
#Order from lower to higher values the average, to plot it nicely

ippu_seed_set <- rbind(ippu_seed_set, ippu_50, ippu_100)
ippu_seed_set$Treatment<- as.character(ippu_seed_set$Treatment)
ippu_seed_set <- ippu_seed_set[order(ippu_seed_set$Treatment),]

@@

library(stringr)
ippu_seed_set_div <- str_split_fixed(as.character(ippu_seed_set$Treatment), " ", 2)
ippu_seed_set_div <- data.frame(ippu_seed_set_div, stringsAsFactors = F)
colnames(ippu_seed_set_div)=c("non_focal","percentage")
ippu_seed_set_bind <- cbind(ippu_seed_set,ippu_seed_set_div)
ippu_seed_set_bind <- filter(ippu_seed_set_bind, percentage!="100%")

#Because I want to give it specifically order I do it separately
#pein_seed_set_common <- filter(ippu_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))

ippu_seed_set_cross <- filter(ippu_seed_set_bind, Treatment %in% c("cross"))
ippu_seed_set_self <- filter(ippu_seed_set_bind, Treatment %in% c("self"))
ippu_seed_set_control <- filter(ippu_seed_set_bind, Treatment %in% c("control"))
ippu_seed_set_flower <- filter(ippu_seed_set_bind, Treatment %in% c("flower control"))

@@

# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
ippu_seed_set_bind=ippu_seed_set_bind[ippu_seed_set_bind$Treatment!=c("cross"),]
ippu_seed_set_bind=ippu_seed_set_bind[ippu_seed_set_bind$Treatment!=c("self"),]
ippu_seed_set_bind=ippu_seed_set_bind[ippu_seed_set_bind$Treatment!=c("control"),]
ippu_seed_set_bind=ippu_seed_set_bind[ippu_seed_set_bind$Treatment!=c("flower control"),]

ippu_seed_set_final<-rbind(ippu_seed_set_bind,ippu_seed_set_cross, ippu_seed_set_self, ippu_seed_set_control,
                           ippu_seed_set_flower)
#deleting extra columns used for data formating
ippu_seed_set_final=ippu_seed_set_final[,-c(5,6)]
#adding NA'S to the focal species
ippu_seed_set_final[ippu_seed_set_final$Treatment==c("IPPU 50%"),4] <- NA

#changing non_focal species name
ippu_seed_set_final$Treatment=as.character(ippu_seed_set_final$Treatment)
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="IPPU 50%"] <- "Brassicaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"

ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"

ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="cross"] <- "Cross"
ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="self"] <- "Self"
ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="control"] <- "Control"
ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="flower control"] <- "Flower control"

#Different colour per family
b <- ggplot(ippu_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Ipomea purpurea",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

#There are 3 crosses were seeds were lost (2,7,9)
#load libraries

#read data and cleaning

gl <- lapply(list(a,b), ggplotGrob)
library(grid)
widths <- do.call(unit.pmax, lapply(gl, "[[", "widths"))
heights <- do.call(unit.pmax, lapply(gl, "[[", "heights"))
lg <- lapply(gl, function(g) {g$widths <- widths; g$heights <- heights; g})

grobz <- lapply(list(a, b), ggplotGrob)
grobz.plot <- arrangeGrob(grobs = list(rbind(grobz[[1]], size = "last"),
                                        rbind(grobz[[2]], size = "last")), ncol = 2,top="hhsdgsujhdg")
